### 2022-11-01 Papers/ICCC-2023/sections/design.tex
spellcheck

The \lstinline{attach} method is called after names of all the program elements have been gathered, but before the compiler starts to analyze function bodies.
It is common accross all attribute targets and accepts the descriptor of the attached program element (function, field, type, etc.).
Only during call to \lstinline{attach} can the attribute change aspects of the program that affect function overload resolution, for example
whether a function is invokable at run or compile time.

@@

One of the possible solutions to the above-mentioned problem is to limit which functions can be invoked at compiletime.
C-=-1 allows code within a compiletime context to invoke procedures only from other packages, declared explicitly as dependencies.
Circular references between packages, as in most other languages, are forbiden.
C-=-1 additionally prohibits modification of dependencies.
Therefore, its is impossible for a function to modify a procedure it depends on.

>>>>

The \lstinline{attach} method is called after names of all the program elements have been gathered, but before the compiler starts to analyze function bodies.
It is common across all attribute targets and accepts the descriptor of the attached program element (function, field, type, etc.).
Only during call to \lstinline{attach} can the attribute change aspects of the program that affect function overload resolution, for example
whether a function is invokable at run or compile time.

@@

One of the possible solutions to the above-mentioned problem is to limit which functions can be invoked at compiletime.
C-=-1 allows code within a compiletime context to invoke procedures only from other packages, declared explicitly as dependencies.
Circular references between packages, as in most other languages, are forbidden.
C-=-1 additionally prohibits modification of dependencies.
Therefore, its is impossible for a function to modify a procedure it depends on.

### 2022-11-01 Papers/ICCC-2023/sections/implementation.tex
spellcheck

The most primitive types within the hierarchy are \lstinline{StringValue} and \lstinline{IntegerValue}.
They are simple wrappers for strings and integers, present in the host language.
Floating point numbers were not implemented as they were not nessecary for implementation of a basic compiler.

@@

C-=-1 language model divides the user program into assemblies.
They represent an individual program package: a library or an executable file.
The compiler is invoked to compile an assembly, together with its dependencies.
Assembly is the root object of C-=-1 program model, it stores a list of assemblies it depends on and the root namespace of the package it represents.
The remainder of user code is organised into namespaces, types, functions and fields.
These parts of the model are repesented by native classes of the host language and form the basis for the rest of the model.

@@

The C-=-1 Backend interface uses LLVM \cite{llvmir} code generation API that has been exposed by the compiler.
The functionality which has been made available to C-=-1 represents a minimal subset of LLVM, that is sufficent to implement a basic compiler.

@@

Certain other intrinsic operations are defined using external dependencies.
C-=-1 memory managment library, in the runtime context, uses a simple interface capable of allocating and deleting a continous buffer.
It consists of two functions: \lstinline{unsafe_new} and \lstinline{delete}.
In the standard library, they are explicitly mapped to \lstinline{malloc} and \lstinline{free} functions from the C runtime.

>>>>

The most primitive types within the hierarchy are \lstinline{StringValue} and \lstinline{IntegerValue}.
They are simple wrappers for strings and integers, present in the host language.
Floating point numbers were not implemented as they were not necessary for implementation of a basic compiler.

@@

C-=-1 language model divides the user program into assemblies.
They represent an individual program package: a library or an executable file.
The compiler is invoked to compile an assembly, together with its dependencies.
Assembly is the root object of C-=-1 program model, it stores a list of assemblies it depends on and the root namespace of the package it represents.
The remainder of user code is organised into namespaces, types, functions and fields.
These parts of the model are represented by native classes of the host language and form the basis for the rest of the model.

@@

The C-=-1 Backend interface uses LLVM \cite{llvmir} code generation API that has been exposed by the compiler.
The functionality which has been made available to C-=-1 represents a minimal subset of LLVM, that is sufficient to implement a basic compiler.

@@

Certain other intrinsic operations are defined using external dependencies.
C-=-1 memory management library, in the runtime context, uses a simple interface capable of allocating and deleting a continuous buffer.
It consists of two functions: \lstinline{unsafe_new} and \lstinline{delete}.
In the standard library, they are explicitly mapped to \lstinline{malloc} and \lstinline{free} functions from the C runtime.
